GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-10-16 ennv.tex
update

The output of a DNN is obtained by iteratively computing  the  values  of  neurons  in  each  layer.
The value of a neuron in the input layer is the input data. The value of a neuron in the hidden layers is computed by applying an \emph{affine transformation} (\autoref{sec:affine}) to values of neurons in the previous layers, then followed by an \emph{activation function} (\autoref{sec:activation}) such as the popular Rectified Linear Unit (ReLU) activation.

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=0.5\linewidth]{figure/dnn.pdf}
%     \caption{\label{fig:dnn} An FNN with ReLU.}
% \end{figure}

@@

\section{Properties of Neural Networks}

\subsection{Robustness}

\subsection{Safety}

>>>>

The output of a DNN is obtained by iteratively computing  the  values  of  neurons  in  each  layer.
The value of a neuron in the input layer is the input data. The value of a neuron in the hidden layers is computed by applying an \emph{affine transformation} (\autoref{sec:affine}) to values of neurons in the previous layers, then followed by an \emph{activation function} (\autoref{sec:activation}) such as ReLU and Sigmoid. The value of a neuron in the output layer is computed similarly but may skip the activation function.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{figure/dnn.pdf}
    \caption{\label{fig:dnn} An FNN with ReLU.}
\end{figure}

@@

\section{Properties of Neural Networks}
Similar to software programs, neural networks have desirable properties to ensure the network behaves as expected. These could be specific to the applications modeled by the network, e.g., safety properties in a collision avoidance system or general properties that are desired by all networks, e.g., robustness to adversarial attacks.

\paragraph{Robustness Properties}
\emph{Robustness}, a desirable property for all networks, ensures that small perturbations in the input data do not cause major changes in the output of the network. For example, if a few pixels in an image are changed, the network should still classify the image correctly. \emph{Adversarial attacks} are a common way to test the robustness of a neural network. In an adversarial attack, an attacker makes small changes to the input data to cause the network to misclassify the data.

\emph{Local} robustness refers to robustness of a neural network within a \emph{small neighborhood or region} of the input data. In contrast, \emph{global} robustness refers to robustness of a network across the \emph{entire input space}. Global robustness is harder to achieve than local robustness, as it requires the network to be robust to all possible inputs.

\paragraph{$\epsilon$-robustness} A neural network is $\epsilon$-robust if the difference between any two inputs $x$ and $x'$ is within a small range $\epsilon$, the output $f$ of the network does not change significantly (or remain the same), i.e., $\|x-x'\| \leq \epsilon \implies f(x) \approx f(x')$.

\paragraph{Safety Properties} Safety properties are specific to the application modeled by the network. For example, a safety property in a collision avoidance system might be that if the intruder is distant and significantly slower than us, then we stay below a certain threshold, i.e., $d_{intruder} > d_{threshold} \land v_{intruder} < v_{threshold} \implies v_{us} < v_{threshold}$.

\subsection{Challenges}

\paragraph{Formalization}

\paragraph{Expressiveness}
